TGI plots

### 2022-04-22 analysis/tgispine_og-plots-exp1.Rmd
running anova to extract information about relative effect size, now to do with lme

# Libraries
```{r warning = FALSE}
library(readr)
library(ggplot2)
library(reshape2)
library(tidyr)
library(dplyr)
```

@@

# Summary
```{r}
n_stim <- df %>% count(id = df$id, dermatome = df$dermatome, location_cold = df$location_cold, stim = df$stim) # number of stimuli per condition
df_median <- aggregate(list(cold = df$cold, warm = df$warm, pain = df$pain), by = list(id = df$id, dermatome = df$dermatome, location_cold = df$location_cold), FUN = median)
df_median
```
# Analysis and effect sizes
```{r}
# cold ratings anova

# cold ratings linear mixed model
# warm ratings anova
# warm ratings linear mixed model
```

@@

# set a figure directory
#figdir<-"~/Dropbox/!Projects/2017_TGI_ginty/figure/"
# dpi resolution
resolution = 600
```
# Figure 1: cold ratings
```{r}
p1 <-ggplot(df_median, aes(x = interaction(location_cold,dermatome), y = cold, fill = dermatome))+
   theme_bw()+
   variance_theme+
   #geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5)+
   geom_boxplot(outlier.shape = NA, notch = FALSE)+ 
   geom_point(aes(x = interaction(location_cold,dermatome), fill = dermatome), shape = 21, size = 3)+
   scale_x_discrete(labels=c("Distal", "Proximal", "Caudal", "Rostral"))+
   scale_y_continuous(limits = c(0,100))+
   guides(fill = FALSE)+
   scale_fill_brewer(palette = "Blues", direction = 1) +
   theme(legend.position="none")+
   ylab("Cold Ratings")+
   xlab("")
p1

@@

# Figure 2: warm ratings
```{r}
p2 <-ggplot(df_median, aes(x = interaction(location_cold,dermatome), y = warm, fill = dermatome))+
   theme_bw()+
   variance_theme+
   #geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5)+
   geom_boxplot(outlier.shape = NA, notch = FALSE)+ 
   geom_point(aes(x = interaction(location_cold,dermatome), fill = dermatome), shape = 21, size = 3)+
   scale_x_discrete(labels=c("Distal", "Proximal", "Caudal", "Rostral"))+
   scale_y_continuous(limits = c(0,100))+
   guides(fill = FALSE)+
   scale_fill_brewer(palette = "Reds", direction = -1) +
   theme(legend.position="none")+
   ylab("Warm Ratings")+
   xlab("")
p2

@@

```
# Figure 3: pain ratings
```{r}
p3 <-ggplot(df_median, aes(x = interaction(location_cold,dermatome), y = pain, fill = dermatome))+
   theme_bw()+
   variance_theme+
   #geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5)+
   geom_boxplot(outlier.shape = NA, notch = FALSE)+ 
   geom_point(aes(x = interaction(location_cold,dermatome), fill = dermatome), shape = 21, size = 3)+
   scale_x_discrete(labels=c("Distal", "Proximal", "Caudal", "Rostral"))+
   scale_y_continuous(limits = c(0,100))+
   guides(fill = FALSE)+
   scale_fill_brewer(palette = "Purples", direction = -1) +
   theme(legend.position="none")+
   ylab("Pain Ratings")+
   xlab("")
p3

>>>>

# Libraries
```{r warning = FALSE}
library(readr)
library(ggplot2)
library(reshape2)
library(tidyr)
library(dplyr)
library(ez)
```

@@

# Summary
```{r}
n_stim <- df %>% count(id = df$id, dermatome = df$dermatome, location_cold = df$location_cold, stim = df$stim) # number of stimuli per condition
df_median <- aggregate(list(cold = df$cold, warm = df$warm, pain = df$pain), by = list(id = df$id, dermatome = df$dermatome, location_cold = df$location_cold), FUN = median)
df_median

# normalise the vas ratings, then summarise - does this change effect size?
# create frame for new dataframe
df_norm <- data.frame(matrix(ncol = 12, nrow = 0))
# index through each participant
for (id_idx in 1:nrow(count(df, id))) {
  id_idx = id_idx+1 # there is no id=1
  tmp <- df[df$id == id_idx ,]

  # find the max value for each VAS ratings
  max_cold <- max(tmp$cold, na.rm = TRUE)
  max_warm <- max(tmp$warm, na.rm = TRUE)
  max_pain <- max(tmp$pain, na.rm = TRUE)
  # then normalise all
  tmp$ncold <- tmp$cold/max_cold
  tmp$nwarm <- tmp$warm/max_warm
  tmp$npain <- tmp$pain/max_pain

  # compile all into one data-frame
  df_norm <- rbind(df_norm, tmp)
}

# summary
df_nmedian <- aggregate(list(cold = df_norm$ncold, warm = df_norm$nwarm, pain = df_norm$npain), 
                        by = list(id = df_norm$id, dermatome = df_norm$dermatome, 
                                  location_cold = df_norm$location_cold), FUN = median)
```
# Analysis and effect sizes
```{r}
# cold ratings anova
cold_anova <- ezANOVA(
  data = df_nmedian
  , dv = .(cold)
  , wid = .(id)
  , within = .(dermatome, location_cold),
  return_aov = TRUE,
  detailed = TRUE
)

# cold ratings linear mixed model
# warm ratings anova
warm_anova <- ezANOVA(
  data = df_nmedian
  , dv = .(warm)
  , wid = .(id)
  , within = .(dermatome, location_cold),
  return_aov = TRUE,
  detailed = TRUE
)

# warm ratings linear mixed model
```

@@

# set a figure directory
#figdir<-"~/Dropbox/!Projects/2017_TGI_ginty/figure/"
# dpi resolution
resolution = 600
```
# Figure 1: cold ratings
```{r}
p1 <-ggplot(df_nmedian, aes(x = interaction(location_cold,dermatome), y = cold, fill = dermatome))+
   theme_bw()+
   variance_theme+
   #geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5)+
   geom_boxplot(outlier.shape = NA, notch = FALSE)+ 
   geom_point(aes(x = interaction(location_cold,dermatome), fill = dermatome), shape = 21, size = 3)+
   scale_x_discrete(labels=c("Distal", "Proximal", "Caudal", "Rostral"))+
   scale_y_continuous(limits = c(0,1))+
   guides(fill = FALSE)+
   scale_fill_brewer(palette = "Blues", direction = 1) +
   theme(legend.position="none")+
   ylab("Cold Ratings")+
   xlab("")
p1

@@

# Figure 2: warm ratings
```{r}
p2 <-ggplot(df_nmedian, aes(x = interaction(location_cold,dermatome), y = warm, fill = dermatome))+
   theme_bw()+
   variance_theme+
   #geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5)+
   geom_boxplot(outlier.shape = NA, notch = FALSE)+ 
   geom_point(aes(x = interaction(location_cold,dermatome), fill = dermatome), shape = 21, size = 3)+
   scale_x_discrete(labels=c("Distal", "Proximal", "Caudal", "Rostral"))+
   scale_y_continuous(limits = c(0,1))+
   guides(fill = FALSE)+
   scale_fill_brewer(palette = "Reds", direction = -1) +
   theme(legend.position="none")+
   ylab("Warm Ratings")+
   xlab("")
p2

@@

```
# Figure 3: pain ratings
```{r}
p3 <-ggplot(df_nmedian, aes(x = interaction(location_cold,dermatome), y = pain, fill = dermatome))+
   theme_bw()+
   variance_theme+
   #geom_hline(yintercept=0, linetype="dashed", color = "black", size=0.5)+
   geom_boxplot(outlier.shape = NA, notch = FALSE)+ 
   geom_point(aes(x = interaction(location_cold,dermatome), fill = dermatome), shape = 21, size = 3)+
   scale_x_discrete(labels=c("Distal", "Proximal", "Caudal", "Rostral"))+
   scale_y_continuous(limits = c(0,1))+
   guides(fill = FALSE)+
   scale_fill_brewer(palette = "Purples", direction = -1) +
   theme(legend.position="none")+
   ylab("Pain Ratings")+
   xlab("")
p3
